dispRity demo for ecological data

### 2015-10-08 doc/dispRity-ecology-demo.Rnw

<<data, fig.width=8, fig.height=8, out.width='.8\\linewidth'>>=
## Loading demo and the package data
library(dispRity)
## let's use the matrix from McClean (unpubl.)
data(McClean_data)
## This dataset contains an ordinated matrix (in 20 dimensions) of the distance
## between experimental plots.
ord_matrix <- McClean_data$ordination
## As well as two list of different factors affecting each experimental plot:
## the treatment and the depth.
treatments <- McClean_data$treatment
depth <- McClean_data$depth
@

@@

<<summary>>=
## The default:
summary(disparity_BS)
## The CIs are calculated as 50 and 95 and the central tendency is the mean by default.
## But we can specify different options
summary(disparity_BS, CI=90, cent.tend=median)

@@

<<rare plots, fig.width=10, fig.height=5, out.width='1\\linewidth'>>=
## Graphical options
quartz(width = 10, height = 5) ; par(mfrow = (c(1,2)), bty = "n")
## The same but looking at the number of plots
plot(disparity_rare, diversity = TRUE)
## With the same number of plots per group
plot(disparity_rare, diversity = TRUE, rarefaction = 17)
@

>>>>

<<data>>=
## Loading demo and the package data
library(dispRity)
## let's use the matrix from McClean (unpubl.)
data(McClean_data)
## This dataset contains an ordinated matrix (in 20 dimensions) of the distance
## between experimental plots.
ord_matrix <- McClean_data$ordination
## As well as two list of different factors affecting each experimental plot:
## the treatment and the depth.
treatments <- McClean_data$treatment
depth <- McClean_data$depth
@

@@

<<summary>>=
## The default:
summary(disparity_BS)
## The quantiles are calculated as 50 and 95 and the central tendency is the mean by default.
## But we can specify different options
summary(disparity_BS, quantile=90, cent.tend=median)

@@

<<rare plots, fig.width=10, fig.height=5, out.width='1\\linewidth'>>=
## Graphical options
quartz(width = 10, height = 5) ; par(mfrow = (c(1,2)), bty = "n")
## The same but looking at the number of plots
plot(disparity_rare, elements = TRUE)
## With the same number of plots per group
plot(disparity_rare, elements = TRUE, rarefaction = 17)
@
